Contracts for Contracts

### 2023-02-28 paper.tex
intro misc

Despite hindsight effort to audit, certify, or verify smart contract programs,
language designers are responsible to provide better languages so that
programmers are able to write invulnerable smart contracts in the first place.
In this paper, we argue that advanced \emph{behavioral contracts} provide a
lightweight linguistic solution for many security issues found in smart
contract programs.

>>>>

Apart from investigating effort to audit, certify, or verify smart contract programs,
language designers are responsible to empower programmers with better
linguistic solution to write invulnerable smart contracts in the first place.
In this paper, we argue that advanced \emph{behavioral contracts} provide a
lightweight solution for many security issues found in smart contract programs.
